%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{hyperref} % Hyperlinks
\usepackage{enumitem}
\usepackage{xcolor}

\setlist[itemize]{nosep, topsep=-5mm, leftmargin=2em, label=--}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Max Tromanhauser} % Your name
\address{(857)~$\cdot$~756~$\cdot$~8635 \\ \href{mailto:mtromanhauser@gmail.com}{mtromanhauser@gmail.com}}
\address{\href{https://max.troman.haus}{max.troman.haus}}
% \address{72 E 3rd St, Apt. 5A, New York, NY 10003} % Your address

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{grouping}{Eductation}
\item {\bf Brown University} \hfill Providence, RI \\
    {\em Master of Science in Computer Science} \hfill Expected 2022 -- 2024 \\
    Current GPA: 4.00 / 4.00

\item {\bf University of Pennsylvania} \hfill Philadelphia, PA \\
    {\em Bachelor of Science in Engineering in Computer Science} \hfill 2012 -- 2016 \\
    Cumulative GPA: 3.22 / 4.00 \\
    CIS Senior Design Second Prize Award
\end{grouping}

\iffalse
\hspace*{1mm}{\em Relevant Courses:} Advanced Topics in Algorithms and Complexity \\
\hspace*{2mm}Internet \& Web Systems, Computer Operating Systems, Introduction to Artificial Intelligence

\hspace*{1mm} {\bf Belmont High School} \hfill Belmont, MA \\
\hspace*{1mm} Graduate \hfill June 2012 \\
\hspace*{1mm} Cumulative GPA: 3.84 / 4.00
\fi

%----------------------------------------------------------------------------------------
%   RESEARCH SECTION
%----------------------------------------------------------------------------------------

\begin{grouping}{Academic Research \hfill (In Progress)}

\item {\bf Finding Balance in Unbalanced PSI: A New Construction from Single-Server PIR.} \\
    Chengyu Lin, Zeyu Liu, Peihan Miao, and Max Tromanhauser. \\
    {\em Submitted to PETS 2024}
    \begin{items}
        \item Implemented prototype for experimental evaluation including optimizations to underlying PIR library.
        \item Investigated PSI and PIR literature to specify our precise contributions.
    \end{items}

\item {\bf Updatable PSI Revisited: Deletion, Cardinality, Sum, and Secret Sharing. } \\
    Saikrishna Badrinarayanan, Peihan Miao, Xinyi Shi, Max Tromanhauser, and Ruida Zeng. \\
    {\em To Be Submitted} % to CCS (?)
    \begin{items}
        \item Wrote up formal construction and security proofs.
        \item Contributed to removing amortization of previous construction by observing that the tree \\
            access can be made independent of input.
    \end{items}

\item {\bf \color{blue} Unnamed MPC Project.} \\
    Peihan Miao, Alice Murphy, Akshayaram Srinivasan, Max Tromanhauser, and Nick Young. \\
    {\em To Be Submitted} % to CCS (?)
    \begin{items}
        \item Analyzed concrete communication and computation costs for the protocol.
        \item Suggested composing primal and dual random matrices in PCG construction.
    \end{items}

\end{grouping}

%----------------------------------------------------------------------------------------
%   (ACADMIC) PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{grouping}{Projects \& Activities}

\item {\bf Multiparty Quantum Computation (MPQC) Literature Review}
    \begin{items}
        \item {\em Final project for Special Topics in Secure Computation (taught by Peihan Miao).}
        \item Presented on eight papers covering MPQC, blind quantum computing, and classical MPC with \\
            quantum parties and adversaries.
    \end{items}

\item {\bf Cryptography Reading Group}
    \begin{items}
        \item Contributed to the department's reading group, where members present recent works of interest.
        \item Delivered talks on papers covering quantum pseudorandom states, blind quantum computing, \\
            Impagliazzo's Five Worlds, and pseudorandom correlation generators.
    \end{items}

\item {\bf Quantum Channel Capacity}
    \begin{items}
        \item {\em Final project for Introduction to Quantum Information Science I (taught by Anurug Anshu).}
        \item Delivered joint presentation on capacity and private capacity for quantum channels.
    \end{items}

\item {\bf Post-Quantum Anonymous Signatures}
    \begin{items}
        \item {\em Presentation for Advanced Topics in Cryptography (taught by Anna Lysyanskaya).}
        \item Discussed lattices and lattice assumptions along with a lattice-based signature scheme and \\
            zero knowledge proof system.
    \end{items}

\end{grouping}

%----------------------------------------------------------------------------------------
%   EMPLOYMENT SECTION
%----------------------------------------------------------------------------------------

\begin{grouping}{Employment}

\iffalse
\item {\bf Brown University } \hfill Providence, RI \\
    {\em Research Assistant} \hfill 2023
    \begin{items}
        \item Worked with Peihan Miao on three research projects.
    \end{items}
\fi

\item {\bf Flatiron Health } \hfill New York, NY \\
    {\em Senior Software Engineer, Clinical Research } \hfill 2020 -- 2022 \\
    {\em Software Engineer, Real World Evidence } \hfill 2017 -- 2019
    \begin{items}
        \item Conducted Prospective Clinico-Genomic study.
        \item Collaborated in a highly cross-functional team to deliver oncological research datasets.
        \item Managed an intern as a direct report through a twelve week project.
    \end{items}

\iffalse
\hspace*{3mm}- Conducted Prospective Clinico-Genomic (PCG) study with cross-functional team \\
\hspace*{3mm}- Developed system for sending data quality inquiries to study practices \\
\hspace*{3mm}- Managed an intern as a direct report through a 12 week project
\fi

\iffalse
\hspace*{3mm}- Collaborated in a highly cross-functional team to deliver 11 projects \\
\hspace*{3mm}- Built data pipelines to create oncological research datasets \\
\hspace*{3mm}- Designed and implemented tools to automate team processes
\fi

%------------------------------------------------

\item {\bf Microsoft } \hfill Redmond, WA \\
    {\em Software Engineer, Azure Active Directory} \hfill 2016 -- 2017
\iffalse
\hspace*{3mm}- Refactored reporting features in Active Directory’s UI for performance and usability \\
\hspace*{3mm}- Updated the reporting service deployment system and deployed to sovereign clouds \\
\hspace*{3mm}- Maintained data pipeline that processed billions of events per month
\fi

\end{grouping}

%------------------------------------------------

%----------------------------------------------------------------------------------------
%   TEACHING SECTION
%----------------------------------------------------------------------------------------

\begin{grouping}{Teaching Experience}

\item {\bf Brown University } \hfill Providence, RI \\
    {\em Teaching Assistant, Data Engineering} \hfill 2022
    \begin{items}
        \item Graded student homework and exams.
        \item Held weekly office hours to assist students.
    \end{items}

\item {\bf University of Pennsylvania } \hfill Philadelphia, PA \\
    {\em Head Teaching Assistant, Introduction to Computer Programming} \hfill 2015 -- 2016 \\
    {\em Teaching Assistant, Introduction to Computer Programming} \hfill 2013 -- 2014 \\
    {\em Teaching Assistant, JavaScript} \hfill 2015
    \begin{items}
        \item Hired and managed a staff of sixty teaching assistants.
        \item Taught weekly recitation of twenty students.
        \item Wrote recitation plans, homework assignments, and exam questions.
    \end{items}

% \hspace*{3mm}- Hired and managed staff of 60 teaching assistants \\
% \hspace*{3mm}- Planned and led weekly staff meetings and training sessions \\
% \hspace*{3mm}- Wrote recitation plans and homework assignments
% \hspace*{3mm}- Taught weekly recitation of 20 students \\
% \hspace*{3mm}- Graded student homework and exams \\
% \hspace*{3mm}- Held office hours to assist students

\end{grouping}
%----------------------------------------------------------------------------------------
%   INDUSTRY RESEARCH SECTION
%----------------------------------------------------------------------------------------

\begin{grouping}{Industry Research}

\item {\bf P10.14 ctDNA and Real-World Response (rwR) in Patients With Lung Cancer From A Prospective} \\
    {\bf Real-World Clinico-Genomic (PCG) Study} \\
    A. Vanderwalde, M. Lu, S. Maund, M. Huntley, D. Incerti, A. Fine, K. Tolba, D. Jin, A.
    Bourla, A. Sondhi, \\
    M. Tromanhauser, D. Daniel, J. Tilford, J. Mcfarlane, S. Lakhanpal, G. Oxnard,
    and K. Schulze \\
    {\em Poster presented at the World Conference on Lung Cancer 2021, Virtual.}
    \begin{items}
        \item One of two engineers building data infrastructure for real-world clinical study.
        \item Designed and implemented tool for communicating with participating clinics.
    \end{items}
\hspace{5mm}

\item {\bf Approximating International Myeloma Working Group Uniform Response Criteria to Derive} \\
    {\bf Response for Multiple Myeloma (MM) Patients Using Data from Electronic Health
    Records (EHR)} \\
    R. Foster, M. Tromanhauser, C. Gayer, P. Gonzales, K. Maignan, A. Opong, A. Torres, and K. Carson \\
    {\em Poster presented at the American Society for Hematology Annual Meeting and Exposition
    2019, Orlando, FL.}
    \begin{items}
        \item Implemented and iterated on heuristic for deriving clinical events from lab data.
        \item Wrote up findings for abstract and conference poster alongside co-author.
    \end{items}
\hspace{5mm}

\iffalse
\hspace*{1mm}R. Foster, M. Tromanhauser, et al. Approximating International Myeloma Working Group Uniform Response \\
\hspace*{1mm}Criteria to Derive Response for Multiple Myeloma (MM) Patients Using Data from Electronic Health Records\\
\hspace*{1mm}(EHR). Presented at American Society for Hematology Annual Meeting and Exposition; 2019 Dec 6-9; \\
\hspace*{1mm}Orlando, FL.
\hspace*{1mm}Rebekah B. Foster, Max Tromanhauser, Christopher Gayer, Patrick K. Gonzales, Kathleen Maignan, \\
\hspace*{2mm}Adomah S. Opong, Aracelis Z. Torres, Kenneth R. Carson; Approximating International Myeloma Working Group \\
\hspace*{2mm}Uniform Response Criteria to Derive Response for Multiple Myeloma (MM) Patients Using Data from \\
\hspace*{2mm}Electronic Health Records (EHR). Blood 2019; 134 (Supplement\_1): 4727. doi: \\
\hspace*{2mm}\href{https://doi.org/10.1182/blood-2019-127181}{https://doi.org/10.1182/blood-2019-127181}

\hspace*{1mm}Rebekah B. Foster, {\bf Max Tromanhauser}, Christopher Gayer, Patrick K. Gonzales, Kathleen Maignan, \\
\hspace*{3mm}Adomah S. Opong, Aracelis Z. Torres, Kenneth R. Carson; {\bf Approximating International Myeloma } \\
\hspace*{3mm}{\bf Working Group Uniform Response Criteria to Derive Response for Multiple Myeloma (MM)} \\
\hspace*{3mm}{\bf Patients Using Data from Electronic Health Records (EHR)}. Blood 2019; 134 (Supplement\_1): 4727.

\hspace*{1mm}Vanderwalde, A., Lu, M., Maund, S., Huntley, M., Incerti, D., Fine, A., Tolba, K., Jin, D., Bourla, A., \\
\hspace*{2mm}Sondhi, A., {\bf Tromanhauser, M.}, Daniel, D., Tilford, J., Mcfarlane, J., Lakhanpal, S., Oxnard, G., \\
\hspace*{2mm}Schulze, K. (2021). {\bf P10.14 ctDNA and Real-World Response (rwR) in Patients With Lung} \\
\hspace*{2mm}{\bf Cancer From A Prospective Real-World Clinico-Genomic (PCG) Study}. Journal of Thoracic \\
\hspace*{2mm}Oncology, 16(10), S1005. \href{https://doi.org/10.1016/j.jtho.2021.08.319}{doi:10.1016/j.jtho.2021.08.319}

\hspace*{1mm}Foster, R. B., {\bf Tromanhauser, M.}, Gayer, C., Gonzales, P. K., Maignan, K., Opong, A. S., Torres A. Z., \\
\hspace*{2mm}Carson, K. R. (2019). {\bf Approximating International Myeloma Working Group Uniform Response} \\
\hspace*{2mm}{\bf Criteria to Derive Response for Multiple Myeloma (MM) Patients Using Data from Electronic} \\
\hspace*{2mm}{\bf Health Records (EHR)}. Blood, 134(Supplement\_1), 4727–4727. \href{https://doi.org/10.1182/blood-2019-127181}{doi:10.1182/blood-2019-127181}
\fi

\end{grouping}
%----------------------------------------------------------------------------------------
%   PATENTS SECTION
%----------------------------------------------------------------------------------------

\begin{grouping}{Patents}

\item {\bf Systems and methods for managing clinical trials.} \\
    Alexander Padmos, Angel Leung, Joshua Buddle, Lauren Sutton, Max Tromanhauser, Shannon
    Lee, and \\ Anthony Hogan \\
    {Patent No.: US11742061B2. Publication Date: Aug 29, 2023}

\end{grouping}

%----------------------------------------------------------------------------------------
%   ADD'L INTERESTS SECTION
%----------------------------------------------------------------------------------------

\iffalse
\medskip
\MakeUppercase{{\bf Additional Interests}}
\medskip
\hrule
\fi


% brewing beer? languages?



%----------------------------------------------------------------------------------------
%   SKILLZ SECTION
%----------------------------------------------------------------------------------------

\iffalse
\begin{rSection}{Technical Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & C, Java, JavaScript, Python, Intermediate German \\
Tools & Node.js, Angular.js, Flask, Android, Express, Git, MySQL, Grunt, Arduino \\
\end{tabular}
\end{rSection}
\fi


%----------------------------------------------------------------------------------------
%	OLD PROJECTS SECTION
%	  Ambassador, pirc/penniaa/india/china/etc, PennOS, MoneyMore, Kashaya,
%----------------------------------------------------------------------------------------

\iffalse
\medskip
\MakeUppercase{{\bf Projects}}
\medskip
\hrule

\hspace*{1mm} {\bf The Ambassador } (\href{http://www.penniaa.com/ambassador}{www.penniaa.com/ambassador}) \hfill Summer, 2015 \\
\hspace*{3mm} Blogging platform and social hub for the Penn International Affairs Association \\
\hspace*{3mm} Developed using Flask, Jinja2, and MySQL

%------------------------------------------------

\hspace*{1mm} {\bf Kashaya English Dictionary } \hfill Spring, 2015 \\
\hspace*{3mm} Android app written with a team for Software Design and Engineering

%------------------------------------------------

\hspace*{1mm} {\bf ILMUNC India } (\href{http://www.ilmunc-india.com/}{www.ilmunc-india.com}) \hfill Spring, 2015 \\
\hspace*{3mm} Wrote the front end for the Ivy League Model United Nations Conference India \\
\hspace*{3mm} Developed using Foundation, Grunt, SASS, and JavaScript

%------------------------------------------------

\hspace*{1mm} {\bf PennOS } \hfill Fall, 2014 \\
\hspace*{3mm} Operating system with a basic scheduler, file system, and shell \\
\hspace*{3mm} Wrote with team for Computer Operating Systems (CIS380)

%------------------------------------------------

\hspace*{1mm} {\bf Intro Courses Admin Console } \hfill Jan, 2014 - Jan, 2015 \\
\hspace*{3mm} Added features to interface allowing CIS110 staff to interact with student grades database \\
\hspace*{3mm} Refactored existing code base to allow for easier development

%------------------------------------------------

\hspace*{1mm} {\bf MoneyMore } (\href{http://boiling-falls-3529.herokuapp.com/}{mtrom.github.io/venmore}) \hfill Fall, 2014 \\
\hspace*{3mm} Fall 2014 PennApps team submission that displays social interactions based on your Venmo feed \\
\hspace*{3mm} Developed using Node.js, Express, Angular.js, d3.js, and the Venmo API
\fi

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\iffalse
\begin{rSection}{Section Name}
 Section content\ldots
 \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
 Computer Languages & Prolog, Haskell, AWK, Erlang, Scheme, ML \\
 Protocols \& APIs & XML, JSON, SOAP, REST \\
 Databases & MySQL, PostgreSQL, Microsoft SQL \\
 Tools & SVN, Vim, Emacs
 \end{tabular}
\end{rSection}
\fi

%----------------------------------------------------------------------------------------

\end{document}
